Investigating shape standardization using geometric morphometry of pottery from Iron Age northeastern Taiwan

### 2020-04-17 analysis/paper/paper.Rmd
merge and order the citation in the main text

To answer the question of whether CV values for vessel samples across our three occupational phases are significantly different or not, we used the Modified signed-likelihood ratio (MSLR) test for equality of CVs [@Krishnamoorthy2014]. While previous work has used the @Feltz1996's asymptotic test for the equality of coefficients of variation from k populations [@Lycett2008; @Okumura2014; @Eerkens2000; @Eerkens2001; @Hoggard2017], we prefer the MSLR test for shape variables as a more recent development with lower rates of type I error, better performance with uneven sample numbers, and more power across a range of conditions [@Krishnamoorthy2014].

>>>>

To answer the question of whether CV values for vessel samples across our three occupational phases are significantly different or not, we used the Modified signed-likelihood ratio (MSLR) test for equality of CVs [@Krishnamoorthy2014]. While previous work has used the @Feltz1996's asymptotic test for the equality of coefficients of variation from k populations [@Eerkens2000; @Eerkens2001; @Hoggard2017; @Lycett2008; @Okumura2014], we prefer the MSLR test for shape variables as a more recent development with lower rates of type I error, better performance with uneven sample numbers, and more power across a range of conditions [@Krishnamoorthy2014].
